---
title: "Mini Literate Analysis"
format: html
---

## Introduction 

### About the data

  This data set includes diverse measurements of seawater chemistry along with supporting conductivity, temperature, and depth (CTD) data from the Arctic Ocean near the North Pole. This data was downloaded from the [Arctic Data Centre](https://arcticdata.io/catalog/view/doi:10.18739/A25T3FZ8X)
  
### Setup
```{r}
library(readr)
```

### Read Data

```{r}
bg_chem <- read_csv("data/BGchem2008data.csv")
```
Exploring data

```{r}
colnames(bg_chem)
summary(bg_chem)
unique(bg_chem$Date)

```

## Analysis

### Calculate summary statistics

```{r}
nitrate <- mean(bg_chem$NO3)
nitrite <- mean(bg_chem$NO2)
amm <- mean(bg_chem$NH4)
phos <- mean(bg_chem$P)
```

### Calculate the mean readfield ratio

```{r}
ratio <- (nitrate + nitrite + amm)/phos
```

### Plot ratio 

<!--This is a comment-->

```{r}
#| echo: false
plot(bg_chem$P, bg_chem$NO3 + bg_chem$NO2 + bg_chem$NH4)
```

## Conclusion

The Redfield ratio is `r round(ratio)`
